%====================
% EXPERIENCE A
%====================
\subsection{Computational statistics with Python \hfill October 2020}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Basic concepts of statistics, such as measures of central tendency, dispersion, and probability.
\item Acquire skills to handle and analyze data using Python libraries and tools like Pandas and NumPy.
\item Learn to visually represent data using libraries like Matplotlib and Seaborn.
\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{Introduction to design \hfill June 2020}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Understand the fundamentals of design, such as composition, color, typography, and visual hierarchy.
\item Explore techniques for designing effective and satisfying user interactions.
\item Acquire skills to create design prototypes and conduct usability testing to improve the user experience.
\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{Personal finance \hfill June 2020}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Understand different types of investments, how financial markets work, and how to make informed investment decisions.
\item Strategies for effectively managing debt, such as debt consolidation, interest rate negotiation, and establishing a repayment plan.
\item Develop skills to create a personal budget, track expenses, and make conscious financial decisions.
\end{zitemize}

%====================
% EXPERIENCE D
%====================
\subsection{Oratory and public speaking \hfill April 2020}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Understand how to use body language and gestures to reinforce the message and convey confidence and authority.
\item Learn to structure and organize speeches coherently and convincingly, including introduction, development, and conclusion.
\item Develop skills to move and use stage space appropriately, maintaining audience engagement.
\end{zitemize}

%====================
% EXPERIENCE E
%====================
\subsection{Introduction to the creation of companies and startups \hfill April 2020}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Understand the fundamentals of strategic planning and how to develop a solid business plan.
\item Understand the fundamentals of strategic planning and how to develop a solid business plan.
\item Learn about the financing options available for startups and how to attract investors.
\end{zitemize}

%====================
% EXPERIENCE F
%====================
\subsection{Negotiation techniques \hfill February 2020}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Develop skills in assertive communication and active listening to understand others perspectives and convey own interests.
\item Learn to identify and address conflicts that may arise during a negotiation, using strategies for resolution and mitigation.
\item Explore different alternatives and creative solutions that allow for mutually beneficial agreements.
\end{zitemize}

%====================
% EXPERIENCE G
%====================
\subsection{Personal brand \hfill April 2019}
\subtext{Platzi \hfill Online}
\begin{zitemize}
\item Identify your strengths, values, and goals to build an authentic and consistent personal brand.
\item Define a unique and differentiating value proposition that sets you apart from other professionals and positions you in your area of expertise.
\item Establish and cultivate professional relationships with key individuals in your industry, participating in events and collaborating on relevant projects.
\end{zitemize}

%====================
% EXPERIENCE H
%====================
\subsection{High school leadership program \hfill June 2019}
\subtext{Universidad Adolfo Ibáñez \hfill Santiago, Chile}
\begin{zitemize}
\item Develop self-awareness, confidence, and decision-making skills to lead effectively.
\item Learn to express oneself clearly, persuasively, and respectfully, both verbally and in writing.
\item Develop skills to identify and address challenges, find creative solutions, and make informed decisions.
\end{zitemize}

