%====================
% EXPERIENCE A
%====================
\subsection{{Python programming assistant / Python Programming Summer School\hfill January 2023}}
\subsection{{Python programming assistant / Python Programming Summer School\hfill January 2022}}
\subtext{MIT International Science and Technology Initiatives with Universidad Mayor \hfill Santiago, Chile}
\begin{zitemize}
\item Translate Python explanations from English to Spanish..
\item Providing support in problem-solving and addressing student inquiries.
\item Assisting in organizing and managing the event.

\end{zitemize}

%====================
% EXPERIENCE B
%====================
\subsection{{Research assistant / Machine learning applications in public policy and economics \hfill August --- December 2021}}
\subtext{Universidad Mayor \hfill Online, Chile}
\begin{zitemize}
\item Collaborating in literature review and gathering relevant information.
\item Collecting relevant data for research in public policy and economics.
\item Preprocess the data using techniques such as cleaning, normalization, and encoding of categorical variables.

\end{zitemize}

%====================
% EXPERIENCE C
%====================
\subsection{{Data science Olympics assistant / Data Science Olympics for high school students \hfill August 2021}}
\subtext{Universidad Mayor \hfill Online, Chile}
\begin{zitemize}
\item Collaborate in the planning and organization of the Data Science Olympics for high school students.
\item Provide technical support and guidance to the students during the competition.
\item Evaluate and grade the projects and solutions presented by the students.

\end{zitemize}
